\Title

### 2016-02-21 manuscript/manuscript.tex
Paragraphs describing the simple synthetic application

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-simple-results}
    \caption{
        Results from the inversion of the simple synthetic data.
        (a) The estimated Moho depth.
        (b) The difference between the true model depths
        and the estimated depths.
        (c) The inversion residuals (observed data minus
        the data predicted by the estimate).
        (d) Histogram of the residuals. Also shown are the calculated
        mean and standard deviation (std) of the residuals.
        Note that the data were contaminated with normally distributed
        pseudo-random noise with zero mean and 5 mGal standard deviation.
        (e) Cross-validation curve used to determine the optimal regularization
        parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.00046$ (red triangle).
        (f) Goal function value (Eq.~\ref{eq:goalfunction}) per Gauss-Newton
        iteration showing the convergence of the gradient descent.
    }
    \label{fig:simple-results}
\end{figure*}

>>>>

We separated the synthetic data into training and testing data sets
following Fig.~\ref{fig:grid_separation}.
The training data set is a regular grid of
$N_{lat} \times N_{lon} = 40 \times 50$ points
(a total of $N_{train} = 2000$).
The testing data set is composed of $N_{test} = 5821$ observations.
We used cross-validation to estimate an optimal regularization parameter ($\mu$)
from a set of $N_\mu = 16$ values equally spaced on a logarithmic scale
between $10^{-6}$ and $10^{-1}$.
We ran our regularized inversion on the training data set
for each value of $\mu$,
obtaining 16 Moho depth estimates.
We computed the mean square error (MSE, Eq.~\ref{eq:msemu}) for each estimate.
The final estimated Moho depth is the one that minimizes the MSE.

Fig.~\ref{fig:simple-results} summarizes the inversion results.
Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
after cross-validation.
The recovered model is smooth, indicating that the cross-validation procedure
was effective at estimating an optimal regularization parameter.
Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
The differences appear to be semi-randomly distributed with a maximum
coinciding with a short-wavelength feature in the true model.
The maximum and minimum differences are approximately
2.19 and -2.13 km, respectively.
Fig.~\ref{fig:simple-results}c shows inversion residuals (difference between
the observed and predicted data), in mGal.
The largest residual (in absolute value) coincides with the largest difference
between the true model and the estimate.
The inversion residuals are normally distributed,
as shown in Fig.~\ref{fig:simple-results}d,
with 0.02 mGal mean and a standard deviation of 3.63 mGal.
The cross-validation curve in Fig.~\ref{fig:simple-results}e
shows a clear minimum MSE at $\mu = 0.00046$
(indicated by the red triangle).
Fig.~\ref{fig:simple-results}f shows the convergence of
the Gauss-Newton optimization in eight iterations.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-simple-results}
    \caption{
        Results from the inversion of the simple synthetic data.
        (a) The estimated Moho depth.
        (b) The difference between the true model depths
        and the estimated depths.
        (c) The inversion residuals (observed data minus
        the data predicted by the estimate).
        (d) Histogram of the residuals. Also shown are the calculated
        mean and standard deviation (std) of the residuals.
        Note that the data were contaminated with normally distributed
        pseudo-random noise with zero mean and 5 mGal standard deviation.
        (e) Cross-validation curve used to determine the optimal regularization
        parameter (Eq.~\ref{eq:goalfunction}).
        Both axis are in logarithmic scale.
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.00046$ (red triangle).
        (f) Goal function value (Eq.~\ref{eq:goalfunction}) per Gauss-Newton
        iteration showing the convergence of the gradient descent.
        The y-axis is in logarithmic scale.
    }
    \label{fig:simple-results}
\end{figure*}
